Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2024-02-15 paper/main.tex
Fix footnote

Newer languages, including ones with considerable interest
in the development community, often lack mutation testing tools.  Even
languages with a long history may long lack a working mutation testing
tool; e.g., it was not until 2014 that Haskell had such a tool~\cite{mucheck}. 
Furthermore, the Haskell mutation tool is no longer
supported,\footnote{The last commits or package updates were in 2015, and the
primary author confirms that changes to {\tt haskell-src-ext} since
introduced render it unusable at present.} and it
appears that no successor tool has appeared in the ensuing
years\footnote{There is FitSpec~\cite{FitSpec}, which is maintained,
  but FitSpec does not perform traditional mutation testing or produce
  source code (or bytecode) mutants; it rather
  performs black-box type-aware mutation of function return values.}.
Haskell developers (until now, see below) have no option for
performing true mutation testing.   Similarly, while the R language is
used by more than 2 million statisticians and data scientists, the
only mutation testing tool for R is a prototype-in-progress that
supports a very limited set of mutation operators
(\url{https://github.com/sckott/mutant}); the last update to the tool
was made in late 2021.

>>>>

Newer languages, including ones with considerable interest
in the development community, often lack mutation testing tools.  Even
languages with a long history may long lack a working mutation testing
tool; e.g., it was not until 2014 that Haskell had such a tool~\cite{mucheck}. 
Furthermore, the Haskell mutation tool is no longer
supported,\footnote{The last commits or package updates were in 2015, and the
primary author confirms that changes to {\tt haskell-src-ext} since
introduced render it unusable at present.} and it
appears that no successor tool has appeared in the ensuing
years.\footnote{There is FitSpec~\cite{FitSpec} which is maintained,
  but FitSpec does not perform traditional mutation testing or produce
  source code (or bytecode) mutants; it rather
  performs black-box type-aware mutation of function return values.}
Haskell developers (until now, see below) have no option for
performing true mutation testing.   Similarly, while the R language is
used by more than 2 million statisticians and data scientists, the
only mutation testing tool for R is a prototype-in-progress that
supports a very limited set of mutation operators
(\url{https://github.com/sckott/mutant}); the last update to the tool
was made in late 2021.
